### 2023-06-10 README.Rmd
230610_v05

We also include metrics from machine learning, i.e., the confusion matrix (e.g., @Burger2018). For all of the 5 provided functions, you currently have to have a **none** option in your data. We currently predict, e.g., whether a buy or no-buy was correctly predicted. Information could be used for overestimating and underestimating, respectively, of product purchases.

@@

<li><code>accuracy</code>: $\frac{2 * precision * recall}{precision + recall}$</li>

<li><code>f1</code>: </li>

<li><code>precision</code>: </li>

<li><code>recall</code>: </li>

<li><code>specificity</code>: </li>

@@

<li><code>accuracy</code>: generates the number of correct predicted
choice or no-choice divided by the total number of predictions. Only
possible for a binary output, e.g., buy vs. no-buy correctly
predicted.</li>

<li><code>f1</code>: generates the F1-Score. F1-Score is calculated by
the following formula
$\frac{2 * precision * recall}{precision + recall}$. Only possible for a
binary output, e.g., buy vs. no-buy correctly predicted.</li>

@@

comparison to Metrics

studi seminar für preference measurement techniques --\> often not
getting in touch with *R* before, so wanted to make it easier for them.
this

@@

>>>>

We also include metrics from machine learning, i.e., the confusion
matrix (e.g., @Burger2018). For all of the 5 provided functions, you
currently have to have a **none** option in your data. We currently
predict, e.g., whether a buy or no-buy was correctly predicted.
Information could be used for overestimating and underestimating,
respectively, of product purchases. In the following <code>TP</code>
stands for true positives, <code>FP</code> for false positives,
<code>TN</code> for true negatives, and <code>FN</code> for false
negatives.

@@

<li><code>accuracy</code>: defined as
$\frac{TP + TN}{TP + FP + TN + FN}$. If you specify an optional
<code>Group</code> argument the output is split by groups.</li>

<li><code>f1</code>: defined as
$\frac{2 * precision * recall}{precision + recall}$ or stated
differently by Burger [-@Burger2018] $\frac{2TP}{2TP + FP + FN}$. If you
specify an optional <code>Group</code> argument the output is split by
groups.</li>

<li><code>precision</code>: defined as $\frac{TP}{TP + FP}$. If you
specify an optional <code>Group</code> argument the output is split by
groups.</li>

<li><code>recall</code>: defined as $\frac{TP}{TP + FN}$. If you specify
an optional <code>Group</code> argument the output is split by
groups.</li>

<li><code>specificity</code>: defined as $\frac{TN}{TN + FP}$. If you
specify an optional <code>Group</code> argument the output is split by
groups.</li>

@@

@@

We are teaching a preference measurement seminar for students. Often
these students did not have experience with *R* before or only sparsely.
We teach them to also validate their results and wanted to give them an
easy way on how to do this in *R*. Of course, there are other great
packages which are even faster in running (i.e., @Metrics), however,
these packages need some more data wrangling in order to use the
appropriate functions, which might be a burden or barrier for the one or
the other.

Moreover, as @yang2018 also report, often commercial studies do not use
any validation task. Some market research companies (as far as we have
realized) are not that familiar with *R* yet. Since these functions are
not always implemented in other softwares, this might be one reason why
they do not include one simply because they do not know how to use it
correctly. Having a package to evaluate the validation/ holdout task can
also be beneficial for those companies.

@@

First, we load the package.

```{r}
library("validateHOT")
```

### Example I - CBC

Since *CBC's* are most commonly used between *CBC*, *ACBC*, and
*MaxDiff*, we will provide an example with a *CBC*. Let us begin with a
*CBC* where all of the variables are coded as part-worth, so we need no
interpolation. Let us load the <code>CBC</code> data frame for this
example.

```{r}
data("CBC")
```

The data frame has a total of `r nrow(CBC)` participants and `r ncol(CBC)` columns.

Now imagine you included a validation/ holdout task with three
alternatives as well as an no-buy option. We specify the <code>data</code> argument and the column index of <code>id</code>. Since we also have a *no-buy* alternative in our validation task, we next specify the <code>None</code> argument, otherwise we would have left it empty. Afterwards, we specify the number of products (<code>prod</code>) we include (excluding the *no-buy* alternative), which we define in the next step with the argument <code>prod.levels</code>. If we look back at the data frame, we can see that the first alternative in the holdout task <code>c(4, 9, 19)</code> is composed of the following attribute levels <code>Att1_Lev1</code>, <code>Att2_Lev1</code>, and <code>Att3_Lev5</code>.

As mentioned above, all the attributes are part-worth coded, therefore, we set <code>coding = c(0, 0, 0)</code>. Finally, we specify the method of prefernce measurement technique, which is <code>method = "CBC"</code> in our case and the column index of the actual participant's choice (<code>choice</code>). If you run the code, a data frame called <code>HOT</code> (short form of **H**old**o**ut **t**ask) will be returned to the global environment.

> &#10071; <code>validateHOT</code> is currently just taking indexes instead of column names, please be aware of this. However, you can easily find out the index by using the <code>names()</code> function or by using <code>which()</code> and <code>colnames()</code>. For example, if you want to find out the column index of <code>id</code>, we could also use <code>which(colnames(CBC) == "ID")</code>.

```{r}
createHOT(
  data = CBC,
  id = 1,
  None = 21,
  prod = 3,
  prod.levels = list(c(4, 9, 19), c(8, 12, 17), c(5, 10, 17)),
  coding = c(0, 0, 0),
  method = "CBC",
  choice = 22
)
```

Let us take a glimpse at the output, which shows the total raw utilities for each of the function included in the validation/ holdout task.

```{r}
head(HOT)
```

In the next step, we would like to see how well our model (from which we took the raw utilities) predict the choices in the validation/ holdout task. First, we will test the <code>hitrate()</code> function. We specify the <code>data</code>, the column index of <code>id</code>, the column index of the alternatives (<code>opts</code>; remember we have three alternatives + the *no-buy* alternative), and finally the column index of the choice. We can see that the hitrate of our example is `r round(hitrate(data = HOT, id = 1, opts = c(2:5), choice = 6)[3, 1], digits  = 3)`.

```{r}
hitrate(data = HOT, id = 1, opts = c(2:5), choice = 6)
```

Let us also check the magnitude of the mean absolute error by running the <code>mae()</code> function.

```{r}
mae(data = HOT, id = 1, opts = c(2:5), choice = 6)
```
To cover also one example on how to use the metrics of the confusion matrix, we could test whether our model overestimates the purchase behavior (our model predicts a *buy* although participant opts for a *no* buy) or underestimates it (i.e., model predicts *no-buy* but participant opts for a *buy*). We will test the accuracy of the model by running the <code>accuracy()</code> function.

```{r}
accuracy(data = HOT, id = 1, opts = c(2:5), None = 5, choice = 6)
```
Finally, let us test, how many participants would at least buy one of the three products, assuming that this is one potential assortment we would like to offer to our consumers. We will use the <code>reach()</code> function and use the threshold approach. To specify the bundles we are offering we use the <code>bundles</code> argument in our function.

```{r}
reach(data = HOT, id = 1, bundles = c(2:4), None = 5, method = "threshold")
```

### Example II - CBC with linear coding
